---
title: "Add new fields"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(sf)

googlecrs <- 4326

path <- "/home/ajackson/Dropbox/Rprojects/CityPermits/"

censusdata <- "~/Dropbox/Rprojects/CensusDataframe/"

DF <- readRDS(paste0(path, "MasterPermits.rds"))

#   mask out rows with bad coordinates
maskcoord <- !(is.na(DF$lat) | is.na(DF$lon))
sum(maskcoord)

#  Create a temporary sf data frame for doing the intersects
# set longitudes as the first column and latitudes as the second
dat <- data.frame(Longitude=DF$lon[maskcoord], Latitude=DF$lat[maskcoord], match=DF$match[maskcoord], stringsAsFactors = FALSE)

dat <- st_as_sf(dat, coords=c("Longitude", "Latitude"), crs=googlecrs, agr = "identity")



knitr::opts_chunk$set(echo = TRUE)
```

## Add New Fields

Add the Superneighborhood, blockgroup, population, median age, and income by blockgroup (2016)
Add population and median age by zipcode - or maybe not.
Add Gini index by tract

```{r add superneighborhood}

temp <- readRDS("~/Dropbox/CrimeStats/SuperNeighborhoodPolys.rds") %>% 
  mutate(SNBNAME=str_to_title(SNBNAME))
#   find points in polygons
#   since superneighborhoods don't overlap, let's just grab the array index
#   instead of creating a huge matrix
a <- st_intersects(dat, temp, sparse = TRUE)

# Replace empty values with 89
a <- unlist(replace(a, !sapply(a, length),89))
# Now add super neighborhood 89 as NA
temp[89,] <- temp[88,]
temp$SNBNAME[89] <- "None"

#   Append the super neighborhood field to the data frame
DF$SuperNeighborhood[maskcoord] <- temp$SNBNAME[a]

#saveRDS(DF, "~/Dropbox/CrimeStats/MasterPermits.rds")


```

##   Create blockgroup and then add appropriate fields

Files are:
- HarrisCounty_", yr, ".rds" for 5YR age, race, median income data. yr=10-16
We'll use 2016 as our go to year


```{r blockgroup}

Census <- readRDS(paste0(censusdata, "CensusData/HarrisCounty_16.rds"))

#   Create full block group codes state (48), county (201), tract (6 numbers), blockgroup (1 number)

Census %>% mutate(BlockGrp=paste0("48201", Tract, BlkGrp)) -> Census

DF %>% mutate(BlockGrp=str_sub(block, start=0, end=12)) -> DF

DF <- left_join(DF, Census, by="BlockGrp")



```

##    Add Gini index by tract

```{r Gini}

infile <- "~/Dropbox/Rprojects/CensusDataframe/CensusData/HarrisCounty_Gini_2016.rds"

gini <- readRDS(infile)

DF <- left_join(DF, gini, by="tract")

saveRDS(DF, paste0(path, "MasterPermits_toGini.rds"))

```


##      Calculate centroids for zipcodes and superneighborhoods

```{r centroids}

a <- 
st_centroid(temp)  

saveRDS(a, "~/Dropbox/CrimeStats/SuperNeighborhoodCentroids.rds") 

#   All texas zips
temp <- readRDS(file = "~/Dropbox/Rprojects/CensusDataframe/ZCTA_polygons_2016.rds")

#   strip down to Houston only

temp <- temp %>% rename(Zip=ZCTA5CE10)
temp <- left_join(DF,temp, by="Zip")
a <- temp[!duplicated(temp$Zip),] %>% select(Zip, Shape)
a <- st_sf(a)
a <- st_centroid(a)
saveRDS(a, "~/Dropbox/CrimeStats/ZipcodeCentroids.rds") 

```














