---
title: "Merge and Clean weekly updates"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)


path <- "/home/ajackson/Dropbox/Rprojects/CityPermits"

knitr::opts_chunk$set(echo = TRUE)
```

##  Read in and merge weekly update files

```{r merge files}

# Read files in, do date and numeric conversion, and then join together

DF <- list.files(path=path, pattern="^20[12].*rds$") %>%
  purrr::set_names(.) %>%
  map_dfr(readRDS) %>%
  rename(Description=Comments, Date=Permit_Date) %>% 
  mutate(Date=as.Date(Date, format= "%Y/%m/%d"),
         lat=as.numeric(lat),
         lon=as.numeric(lon))

```

##  Look for nulls

Looks like nulls fall into the derived geolocations, due to a failure of the
geocoder to find the address. Looks like about 15% failure rate. Not too bad.

```{r nulls}

#   Nulls?

DF %>%
    map_df(function(x) sum(is.na(x))) %>%
    gather(feature, num_nulls) %>%
    print(n = 100)

```


##  Zipcode

Look at zipcodes for issues. Looks okay.

```{r zipcodes}

sort(unique(DF$Zip))

```

##  Dates

Look at Dates for issues. Looks okay.

```{r date}

sort(unique(DF$Date))

```

##  Permit type

Look at Permit Type for issues. Looks okay.

```{r permit type}

sort(unique(DF$Permit_Type))

```

##   Fix Clutch City

Census geocoder likes to put "Clutch City" instead of Houston for addresses downtown.
Really irritating. We'll fix it.

```{r clutch city}

a <- DF %>% mutate(clutch=grepl("CLUTCH", match)) %>% select(clutch)
sum(a$clutch)

DF$match <- str_replace(DF$match, "CLUTCH CITY", "HOUSTON")

```

##  Save file

Save out to a master file

```{r save}

saveRDS(DF, paste0(path, "/MasterPermits.rds"))

```

##    Make Icon file

```{r icons}

colorIcons <- iconList(
  blue = makeIcon("~/Dropbox/Rprojects/CityPermits/marker-icon-blue.png"),  
  black = makeIcon("~/Dropbox/Rprojects/CityPermits/marker-icon-black.png"),  
  green = makeIcon("~/Dropbox/Rprojects/CityPermits/marker-icon-green.png"),  
  grey = makeIcon("~/Dropbox/Rprojects/CityPermits/marker-icon-grey.png"),  
  red = makeIcon("~/Dropbox/Rprojects/CityPermits/marker-icon-red.png"),  
  violet = makeIcon("~/Dropbox/Rprojects/CityPermits/marker-icon-violet.png"),  
  yellow = makeIcon("~/Dropbox/Rprojects/CityPermits/marker-icon-yellow.png")  
  )

saveRDS(colorIcons, "~/Dropbox/Rprojects/CityPermits/colorIcons.rds")

```




